---
title: "Intermediate R"
author: "Lucas Shen"
date: "August 14, 2015"
output: html_document
---

```{r message=F}
library(dplyr)
```
***

### `lapply(x, FUN, ...)`
> like python's `map`, return `list`
> good for heterogeneous data, but sometimes unneccesary

```{r}
1:10 %>% lapply(function(x) x^2) %>% unlist()
```

> we have `funciton(x,y)` here, the vector would pipe in the first argument, and we have to specify the second one by name = val

```{r}
1:10 %>% lapply(function(base, power) base^power, power=2) %>% unlist()
1:10 %>% lapply(function(base, power) base^power, power=3) %>% unlist()
```

###`sapply(X, FUN, ..., simplify = TRUE, USE.NAMES = TRUE)`
> try to simply the output for you, 

###`vapply(X, FUN, FUN.VALUE, ..., USE.NAMES = TRUE)`
> you have to specify output format, it makes it a safer alternative of sapply
> 
> so the `FUN.VALUE` is where you explicityly specify what you expect your function to return.

> usually, you name elements in the return vector

```{r eval=F}
data %>% vapply(func, character(2)) # func should return vec 2 strings
```

***
#Useful functions
###math
```{r eval=F}
abs()

round()

sum()

mean()
```

###data structure
```{r eval=F}
rep( seq, times = n) # repeat as a whole 123 -> 123123

rep( seq, each = n) # repeat element wise 123 -> 112233

seq(start, end, by = k)

str()

is.*() # check type

as.*() # convert to type

unlist() # -> vector

rev()
```

###regular expressions
```{r}

```













