---
title: "static ggvis"
author: "Lucas Shen"
date: "August 7, 2015"
output: html_document
---
```{r, message=FALSE}
library(ggvis)
library(dplyr)
```
***

###make line chart between mpg and wt, find approx line for each group by cyl
```{r}
mtcars %>% 
  group_by(cyl) %>%
  ggvis(~mpg, ~wt) %>% 
  layer_smooths(stroke = ~factor(cyl)) %>% 
  layer_points()
```

###make density chart and color for different group of cyl
* pay attention to the `~factor(var)` part. This is how we could directly handle transformed variable.
```{r}
mtcars %>% group_by(cyl) %>% ggvis(~mpg) %>% layer_densities(fill = ~factor(cyl))
```

###group_by more than one `var`
* you can see that we are still coloring by cyl factor
```{r}
mtcars %>% group_by(cyl, am) %>% ggvis(~mpg, fill = ~factor(cyl)) %>% layer_densities()
```

###with `interaction()`
* `interaction()` is a way to map `ggvis` properties to a combination of `var`s, so in this way, we could color the graph by every (cyl, am) combination
```{r}
mtcars %>% group_by(cyl, am) %>% ggvis(~mpg, fill = ~interaction(cyl, am)) %>% layer_densities()
```

***

##Multi-layer plot
2 points here:

1. we should seperate properties for different layers to create the real visual effect you want
2. put all those common property into ggvis()

```{r}
pressure %>% 
  ggvis(~temperature, ~pressure, stroke := "skyblue",strokeOpacity := 0.5, strokeWidth := 5) %>% 
  layer_lines() %>% 
  layer_points(fill = ~temperature, shape := "triangle-up", size := 300)
```

```{r}
pressure %>% 
  ggvis(~temperature, ~pressure) %>%
  layer_lines(opacity := 0.5) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm", stroke := "navy") %>%
  layer_smooths(stroke := "skyblue")
```











