---
title: "static ggvis"
author: "Lucas Shen @sqor"
date: "August 9, 2015"
output: html_document
---
```{r, message=FALSE}
library(ggvis)
library(dplyr)
```
***

###Make line chart between mpg and wt, find approx,smooth line for each group by cyl
```{r}
mtcars %>% 
  group_by(cyl) %>%
  ggvis(~mpg, ~wt) %>% 
  layer_smooths(stroke = ~factor(cyl)) %>% 
  layer_points()
```

###Make density chart and color by different group of cyl
* pay attention to the `~factor(var)` part. This is how we could directly handle transformed variable.
```{r}
mtcars %>% group_by(cyl) %>% ggvis(~mpg) %>% layer_densities(fill = ~factor(cyl))
```

###`group_by` more than one `var`
* you can see that we are still coloring by cyl factor
```{r}
mtcars %>% group_by(cyl, am) %>% ggvis(~mpg, fill = ~factor(cyl)) %>% layer_densities()
```

###with `interaction()`
* `interaction()` is a way to map `ggvis` properties to a combination of `var`s, so in this way, we could color the graph by every (cyl, am) combination
```{r}
mtcars %>% group_by(cyl, am) %>% ggvis(~mpg, fill = ~interaction(cyl, am)) %>% layer_densities()
```

***

###Multi-layer plot
2 points here:

1. we should seperate properties for different layers to create the real visual effect you want
2. put all those common property into ggvis()

```{r}
pressure %>% 
  ggvis(~temperature, ~pressure, stroke := "skyblue",strokeOpacity := 0.5, strokeWidth := 5) %>% 
  layer_lines() %>% 
  layer_points(fill = ~temperature, shape := "triangle-up", size := 300)
```

```{r}
pressure %>% 
  ggvis(~temperature, ~pressure) %>%
  layer_lines(opacity := 0.5) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm", stroke := "navy") %>%
  layer_smooths(stroke := "skyblue")
```

***
###axes and legends
* add modified axes, attention on `value` and `subdivide` to control tick mark.
```{r}
faithful %>% 
  ggvis(~waiting, ~eruptions) %>% 
  layer_points() %>% 
  add_axis("y", title = "Duration of eruption (m)", 
          values = c(2, 3, 4, 5), subdivide = 9) %>% 
  add_axis("x", title = "Time since previous eruption (m)",
          values = seq(50,90, by=10), subdivide = 1)
```

***

1. now I know `~factor(var)` could be used to transform var in so many place
2. `'fill'` here refer to `scales` arguement of `add_legend`, this is the name of scale for which t oadd a legend. We could use "size", "shape", "fill", "stroke", and we could even use more than one.

```{r}
faithful %>% 
  ggvis(~waiting, ~eruptions, opacity := 0.6, 
        fill = ~factor(round(eruptions))) %>% 
  layer_points() %>%
  add_legend('fill', title = '~duration (m)', orient = 'left')
```

* before consolidate legends, kind of messy
```{r}
faithful %>% 
  ggvis(~waiting, ~eruptions, opacity := 0.6, 
        fill = ~factor(round(eruptions)), shape = ~factor(round(eruptions)), 
        size = ~round(eruptions))  %>%
  layer_points()
```

* after consolidation, see `add_legend(c('fill', 'shape', 'size'))`
```{r}
faithful %>% 
  ggvis(~waiting, ~eruptions, opacity := 0.6, 
        fill = ~factor(round(eruptions)), shape = ~factor(round(eruptions)), 
        size = ~round(eruptions))  %>%
  layer_points() %>%
  add_legend(title = '~ duration (m)', c('fill', 'shape', 'size'))
```

###`scale`
* `scale_numeric()`
* `scale_datetime()`
* `scale_logical()`
* `scale_nominal()`
* `scale_singular()`

***

* use `scale_numeric()` to map property `fill` to a contineuous color range
```{r}
mtcars %>% ggvis(~wt, ~mpg, fill = ~hp) %>%
  layer_points() %>%
  scale_numeric('fill', range = c('beige', 'green'))
```

* `scale_nominal()` :categorical mapping
```{r}
mtcars %>% ggvis(~wt, ~mpg, fill = ~factor(cyl)) %>%
  layer_points() %>%
  scale_nominal("fill", range = c("purple", "blue", "green"))
```

***

###`scale` more than just color
* `scale` can be used not only to color, but to other properties, like `opacity` here
```{r}
mtcars %>% ggvis(x = ~wt, y = ~mpg, fill = ~factor(cyl), opacity = ~hp) %>%
  layer_points() %>%
  scale_numeric('opacity', range = c(0.2,1))
```

* we can even adjust the scale of the value of x, and y axis, see `?scale_numeric` for details
```{r}
mtcars %>% ggvis(~wt, ~mpg, fill = ~disp) %>%
  layer_points() %>%
  scale_numeric("y", domain = c(0, NA)) %>%
  scale_numeric("x", domain = c(0, 6))
```
